---
title: "CANDEV Data Challenge"
author: "Li Ji"
date: "04/02/2022"
output:
  html_document: 
    code_folding: hide
---

Get access to most of the packages that I will use within this RMD file.

```{r}
pacman::p_load(rio, mice, psych, DT, lattice, sjmisc, sjPlot, captioner) # pacman installs packages 
```  

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read the data of INCIDENTS.

```{r }
INCIDENTS <- read.csv("C:/Users/ASUSA/Desktop/CANDEV Data Challenge/SSC dataset/INCIDENTS.csv")
head(INCIDENTS)
describe(INCIDENTS)
```

# Data Cleaning: Missing Value

Have an understanding of the missing values in this dataset.

```{r}
xray::anomalies(INCIDENTS) 
```

For better view of the results for the distribution of missing values.

```{r}
pacman::p_load(inspectdf)
INCIDENTS[, c(2:20)] %>% inspect_na %>% show_plot
```

Delete the columns with 100% and 99.5% missing values.

```{r}
library(tidyverse)
INCIDENTS1 <- select(INCIDENTS, -12, -18)
describe(INCIDENTS1)
xray::anomalies(INCIDENTS1)
```

Delete the rows with missing values accounting for 0.3%, 0.4% and 0.5%, which are pretty small percentages and generally won't affect the results.

```{r}
INCIDENTS2 <- na.omit(INCIDENTS1)
describe(INCIDENTS2)
xray::anomalies(INCIDENTS2)
```

Have an overview of the cleaned dataset.

```{r}
head(INCIDENTS2, 30)
```

# Mean time to restore service (MTRS)

Getting the MTRS to see if there are particular services that are taking longer on average to be restored. Will based on the time of BUSINESS_COMPLETION_HRS.

## Revert BUSINESS_COMPLETION_HRS to Days

```{r}
unique(INCIDENTS2$PRIORITY)
```
Based on definition, to convert hours to days, I divide BUSINESS_COMPLETION_HRS by 24 for high incidents and by 10 for medium and low.

```{r}
INCIDENTS2$BUSINESS_COMPLETION_HRS = ifelse(INCIDENTS2$PRIORITY == "High", INCIDENTS2$BUSINESS_COMPLETION_HRS/24, INCIDENTS2$BUSINESS_COMPLETION_HRS/10 )
head(INCIDENTS2, 30)
```

```{r}
describe(INCIDENTS2$BUSINESS_COMPLETION_HRS)
```

From now on, MTRS is all based on days. Below is the dataset for MTRS according to different Service_Type.

```{r}
MTRS_by_type <- aggregate(INCIDENTS2$BUSINESS_COMPLETION_HRS, list(INCIDENTS2$service), mean )
names(MTRS_by_type) <- c("Service_Type", "MTRS")
MTRS_by_type
```

For better view, I data in descending order for MTRS to find the  services that are taking longer on average to be restored. 

```{r  }
MTRS_by_type[order(MTRS_by_type$MTRS, decreasing = T), ] %>%  datatable( rownames = TRUE, filter="top", class = 'cell-border stripe', options = list(scrollX=T)) %>%  formatRound(columns=c(2), digits=2 ) 
```  

As we can see from above chart, IT Continuity Support Service and Solutions Integration Service (SIS) required extremely longer time on average to be restored, with 421.91 and 117.25 days respectively.


# Correlation between Two Variables
 
Now, I try to find the possible correlation between the number of times an incident is reassigned and how long it takes to restore.   

Read the data of INCIDENT_OWNER_HIS to see the history of ownership of these incidents.

```{r }
INCIDENT_OWNER_HIS <- read.csv("C:/Users/ASUSA/Desktop/CANDEV Data Challenge/SSC dataset/INCIDENT_OWNER_HISTORY.csv")
head(INCIDENT_OWNER_HIS,40)
```

Group the assigned times based on ticket number to see how many times these tickets were assigned.

```{r}
group_by_ticket <- aggregate(
  x= INCIDENT_OWNER_HIS$assigned_group,
  by = list(INCIDENT_OWNER_HIS$ticket_nmbr),
  FUN = function(x) length(unique(x)))
names(group_by_ticket) <- c("ticket_nmbr", "assigned_times")
head(group_by_ticket)
```
Have an idea about the max and min for the assigned times.

```{r}
max(group_by_ticket$assigned_group_nmbr)
min(group_by_ticket$assigned_group_nmbr)
```

Group the Business Completion days by ticket number and to see how many days it took to get these incidents restored.

```{r}
restore_days_by_ticket <- INCIDENTS2[, c("TICKET_NMBR", "BUSINESS_COMPLETION_HRS")]
names(restore_days_by_ticket) <- c("ticket_nmbr", "restore_days")
restore_days_by_ticket
```

Combine the data for Business Completion days and assigned times based on ticket number.

```{r}
times_days<- merge(group_by_ticket,restore_days_by_ticket,by="ticket_nmbr")
times_days
```

There are some extreme outliers, which will affect the results for finding the correlation, so I drop the data with restore_days greater than 600 (just seven rows).

```{r}
times_days_extr <- subset(times_days, times_days$restore_days > 600 )
times_days_extr
```

```{r}
times_days_new <- subset(times_days, times_days$restore_days <= 600 ) 
times_days_new
```

Double comfirm the missing values and its distribution.

```{r}
xray::anomalies(times_days_new)
describe(times_days_new)
```

Visualization with ggcorrplot.

```{r}
#install.packages("ggcorrplot")
library(ggplot2)
library(ggcorrplot)

library("ggpubr")
ggscatter(times_days_new, x = "assigned_times", y = "restore_days", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "assigned_times", ylab = "restore_days")
```

Visualization with psych package.

```{r}
library(psych)
pairs.panels(times_days_new[, 2:3], 
             method = "pearson", # correlation method
             hist.col = "#00AFBB",
             density = TRUE,  # show density plots
             ellipses = TRUE # show correlation ellipses
             )
```

Visualization of scatter plot.

```{r}
attach(times_days_new)
plot(assigned_times, restore_days, main="Scatterplot",
   xlab="assigned_times", ylab="restore_days", pch=19)
```

```{r}
library(car)
#scatterplot(restore_days ~ assigned_times, data=times_days_new,
   #xlab="assigned_times", ylab="restore_days",
   #main="Scatter Plot",
   #labels=row.names(times_days_new$assigned_times))
```

Based on the charts shown above, we can see that there is a slightly positive correlation between the two variables, which means that it normally takes longer time to restore incidents if they are assigned multiple time to different departments.






