---
title: "CANDEV"
output: html_document
---

## look at closure codes for difference between low vs medium priority tickets 
## types of service issues 

# read in data 
```{r}
incidentdf <- read.csv(file = '/Users/kevinpark/Downloads/drive-download-20220204T171629Z-001/INCIDENTS.csv')
historydf <- read.csv(file = '/Users/kevinpark/Downloads/drive-download-20220204T171629Z-001/INCIDENT_HISTORY.csv')
ownerdf <- read.csv(file = '/Users/kevinpark/Downloads/drive-download-20220204T171629Z-001/INCIDENT_OWNER_HISTORY.csv')

# subset by priority 
lowpri <- incidentdf %>%
  filter(str_detect(PRIORITY, "Low"))
medpri <- incidentdf %>%
  filter(str_detect(PRIORITY, "Medium"))
highpri <- incidentdf %>%
  filter(str_detect(PRIORITY, "High"))

priority <- list(incidentdf, lowpri, medpri, highpri, good, bad)
namespriority <- c("incidentdf", "lowpri", "medpri", "highpri")
names(priority) = namespriority





midrange <- incidentdf %>%
  group_by(ASSIGNED_GROUP, service) %>%
  tally() %>%
  filter(str_detect(service, "Midrange - Windows -X86")) %>%
  left_join(incidentdfmeansgroup$incidentdf) %>%
  filter(n > 1289)
gcwan <- incidentdf %>%
  group_by(ASSIGNED_GROUP, service) %>%
  tally() %>%
  filter(str_detect(service, "GC WAN")) %>%
  left_join(incidentdfmeansgroup$incidentdf) %>%
  filter(n >1917)
other <- incidentdf %>%
  group_by(ASSIGNED_GROUP, service) %>%
  tally() %>%
  filter(str_detect(service, "Other - Service Management")) %>%
  left_join(incidentdfmeansgroup$incidentdf)  %>%
  filter(n >554)
View(gcwan)
View(other)
View(midrange)


# prop of types of services by number of incidents 
prop <- incidentdfmeansservice$incidentdf 

sum(prop$`no. of incidents`)
prop$prop <- prop$`no. of incidents`/226296
prop <- prop %>%
    mutate(across(where(is.numeric), ~ round(., 3))) %>%
  filter(prop > 0.028)

View(prop)
sum(prop$prop)
```


# unfinished comparison, compare assigned_groups by proportion of true false of meeting service target between low med high priority tickets
```{r}
lowpri <- incidentdf %>%
  filter(str_detect(PRIORITY, "Low")) %>%
  filter(str_detect(service, "Midrange - Windows -X86")) %>%
  group_by(ASSIGNED_GROUP) %>% 

  
midrange2 <- incidentdf %>%
  group_by(ASSIGNED_GROUP, PRIORITY) %>%
  tally() %>%
  filter(str_detect(ASSIGNED_GROUP, "DC000236")) 
View(lowpri)
  
```


# Is there a correlation between the number of tickets associated with a particular assigned group, organization or service and the time it takes to restore service? service 
## mean and median actual comnpletion hours by SERVICE
```{r}
avehourservice <- function(x){
table1 <- x %>%
  group_by(service) %>%
  tally()
meanhours <- x %>%
  group_by(service) %>%
  select(service, ACTUAL_COMPLETION_HRS) %>%
  mutate_at(vars(ACTUAL_COMPLETION_HRS), ~replace_na(., 0)) %>%
    summarise_each(funs("mean days" = mean)) 
medianhours <- x %>%
    group_by(service) %>%
    select(service, ACTUAL_COMPLETION_HRS) %>%
    mutate_at(vars(ACTUAL_COMPLETION_HRS), ~replace_na(., 0)) %>%
    summarise_each(funs("median days" = median)) 
incidentdfmeans <- table1 %>%
  left_join(meanhours) %>%
  left_join(medianhours) %>%  
  rename("no. of incidents"= "n") 


return(incidentdfmeans)
}

#incidentdfmeans$`mean days` <- lapply(incidentdfmeans$`mean days` ,function(x) x /24)
#incidentdfmeans$`median days` <- lapply(incidentdfmeans$`median days` ,function(x) x /24)


incidentdfmeansservice <- lapply(priority, avehourservice)
View(incidentdfmeansservice$incidentdf)


```


## mean and median actual comnpletion hours by ORGANIZATION
```{r}
avehoursorg <- function(x){
table1 <- x %>%
  group_by(org_id) %>%
  tally()
meanhours <- x %>%
  group_by(org_id) %>%
  select(org_id, ACTUAL_COMPLETION_HRS) %>%
  mutate_at(vars(ACTUAL_COMPLETION_HRS), ~replace_na(., 0)) %>%
    summarise_each(funs("mean hours" = mean)) 
medianhours <- x %>%
    group_by(org_id) %>%
    select(org_id, ACTUAL_COMPLETION_HRS) %>%
    mutate_at(vars(ACTUAL_COMPLETION_HRS), ~replace_na(., 0)) %>%
    summarise_each(funs("median" = median)) 
incidentdfmeans <- table1 %>%
  left_join(meanhours) %>%
  left_join(medianhours) %>%
  mutate(across(where(is.numeric), ~ round(., 1))) %>%
  rename("no. of incidents"= "n") %>%
return(incidentdfmeans)
}

incidentdfmeansorg <- lapply(priority, avehoursorg)

View(incidentdfmeansorg$incidentdf)

```

## mean and median actual comnpletion hours by ASSIGNED GROUP
```{r}
avehoursgroup <- function(x){
table1 <- x %>%
  group_by(ASSIGNED_GROUP) %>%
  tally()
meanhours <- x %>%
  group_by(ASSIGNED_GROUP) %>%
  select(ASSIGNED_GROUP, ACTUAL_COMPLETION_HRS) %>%
  mutate_at(vars(ACTUAL_COMPLETION_HRS), ~replace_na(., 0)) %>%
    summarise_each(funs("mean hours" = mean)) 
medianhours <- x %>%
    group_by(ASSIGNED_GROUP) %>%
    select(ASSIGNED_GROUP, ACTUAL_COMPLETION_HRS) %>%
    mutate_at(vars(ACTUAL_COMPLETION_HRS), ~replace_na(., 0)) %>%
    summarise_each(funs("median hours" = median)) 
incidentdfmeans <- table1 %>%
  left_join(meanhours) %>%
  left_join(medianhours) %>%
  mutate(across(where(is.numeric), ~ round(., 1))) %>%
  rename("no. of incidents"= "n") %>%
return(incidentdfmeans)
}

incidentdfmeansgroup <- lapply(priority, avehoursgroup)
View(incidentdfmeansgroup$incidentdf)
View(incidentdfmeansgroup$lowpri)
View(incidentdfmeansgroup$medpri)
View(incidentdfmeansgroup$highpri)
)



```

# Average time that incidents spend in a particular status. convert to days 
```{r}
# mean hours + number of incidents 
meanhourstatus <- function(x){

table1 <- x %>%
  group_by(STATUS) %>%
  tally()
meanhours <- x %>%
  group_by(STATUS) %>%
  mutate_at(vars(TIME_IN_STATUS_HRS), ~replace_na(., 0)) %>%
  summarise_each(funs("mean hours" = mean)) %>%
    select(-c(2,3))
medianhours <- x %>%
    group_by(STATUS) %>%
    select(STATUS, TIME_IN_STATUS_HRS) %>%
    mutate_at(vars(TIME_IN_STATUS_HRS), ~replace_na(., 0)) %>%
    summarise_each(funs("median hours" = median))
historydfmeans <- table1 %>%
  left_join(meanhours) %>%
  left_join(medianhours) %>%
  mutate(across(where(is.numeric), ~ round(., 1))) %>%
  rename("no. of incidents"= "n") %>%
  rename("mean hours"= "TIME_IN_STATUS_HRS_mean hours")

return(historydfmeans)

}
 
statushourmeans <- meanhourstatus(historydf)
View(statushourmeans)




```

# export to excel
```{r}
list_of_datasets <- list("assigned groups" = incidentdfmeansgroup$incidentdf, "org_id" = incidentdfmeansorg$incidentdf, "statushours" = statushourmeans, "service" = prop, "midrange" = midrange, "gcwan" = gcwan, "other" = other)
write.xlsx(list_of_datasets, file = "candev.xlsx")
```






